---
title: "Covid91 vaccine study Final2020"
author: "Maryana Maayah"
date: "November 3, 2020"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(forcats)
OldData <-read.csv(file="covid91.csv",header=TRUE)
#recode aids to say covid and then remove the annoying "X" from the dataframe
FinalData <- OldData %>% mutate(infected = recode(infected, aids = "covid", none = "OK" )) %>% select(-one_of("X"))
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative vaccine (covid91) is under test in clinical trials. Given the nature of this vaccine it is suspected that the drug may exhibit different effectiveness across the variety of subpopulations tracked. Consider population subgroups by gender( guys and gals), drug use, and sexual orientation. Write a complete report that separately considers this drug for each subgroup and your recommendations as to whether people in the subgroup should take the vaccine.

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

# Results

# Females 

```{r}
dataF=filter(FinalData,sex=='gal')
```

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

```{r}
barchartGC(~infected + treatment,data=dataF)
barchartGC(~infected + treatment,data=dataF, type="percent")

```
The women who got the vaccine are less likely to get Covid-19 than women who got the placebo.

```{r}
table1 <- xtabs(~infected + treatment,data=dataF)
rowPerc(table1)
colPerc(table1)
```

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```
The odds ratio of acquiring Covid-19 is if you have the vaccine is 0.5 to 1 the women who got the vaccine are less likely to get Covid-19 than women who got the placebo, because the 95% in confidence interval is less than 1 we have evidence that the vaccine is effective. 

# Males
  
```{r}
dataM=filter(FinalData,sex=='guy')
```

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

```{r}
barchartGC(~infected + treatment,data=dataM)
barchartGC(~infected + treatment,data=dataM, type="percent")

```

This means that males who got the vaccine were more likely to get Covid-19 than males who got the placebo.

```{r}
table1 <- xtabs(~infected + treatment,data=dataM)
rowPerc(table1)
colPerc(table1)
```

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```
The odds ratio is 1.5 to 1 and that means that males who got the vaccine were 1.5 times more likely to get Covid-19 than males who got the placebo, the 95% confidence interval is more than 1 so we know that the result is significant. 

#  LGBTQ  

```{r}
dataQ=filter(FinalData,LGBTQ=='gay')
```

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

```{r}
barchartGC(~infected + treatment,data=dataQ)
barchartGC(~infected + treatment,data=dataQ, type="percent")

```

That people who got the vaccine were more likely to get Covid-19 than people who got the placebo. 

```{r}
table1 <- xtabs(~infected + treatment,data=dataQ)
rowPerc(table1)
colPerc(table1)
```

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```
The odds ratio is 2.5 to 1 and that means that gay people who got the vaccine were 2.5 times more likely to get Covid-19 than gay people who got the placebo, the 95% confidence interval is more than 1 so we know that the results that came out were important to be worthy of attention in another words sufficiently great which means the vaccine wasn't effective. 

# Drugusers
```{r}
dataD=filter(FinalData,DrugUser=='yes')
```

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

```{r}
barchartGC(~infected + treatment,data=dataD)
barchartGC(~infected + treatment,data=dataD, type="percent")

```

The people who got the vaccine are less likely to get Covid-19 than the people who got the placebo.

```{r}
table1 <- xtabs(~infected + treatment,data=dataD)
rowPerc(table1)
colPerc(table1)
```

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```
The odds ratio of acquiring Covid-19 is if you have the vaccine is 0.5 to 1 the DrugUser who got the vaccine are less likely to get Covid-19 than DrugUser who got the placebo, because the 95% in confidence interval is less than 1 we have evidence that the vaccine is effective. 

# Discussion and Conclusion  

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

In conclusion, the vaccination was only effective for women and drug users since the odd ratio for each of these two categories was 0.5 to 1, which is less than one in other words, and there was evidence that the drug was effective for only these two, it revealed that women and drug users who took the vaccine became less likely to develop Covid-19 in the percentage bar. But if you were a man or a gay person and you were taking the vaccine, you would be more likely than the people who took the placebo to get Covid-19, which indicates that the vaccine was not successful.